---
title: "Regression Models Course Project"
author: "Hatem Jasim Hatem"
date: "May 17, 2019"
output: pdf_document
---
## Introduction   
This work for Motor Trend, a magazine about the automobile industry. Looking at a data set of a collection of cars, they are interested in exploring the relationship between a set of variables and miles per gallon (MPG) (outcome). They are particularly interested in the following two questions:

* Is an automatic or manual transmission better for MPG

* Quantify the MPG difference between automatic and manual transmissions


To answer above questions make exploratory analysis to determine relationship between MPG and Transmission type (Automatic, Manual).

## Exploratory analysis

```{r}
summary(mtcars$mpg)
aggregate(mpg~am, data=mtcars, summary)



```
The exploratory analysis show difference in **MPG** depend on gear transmission types as shown in figure in appendix. This difference is significant depend on T-test p-value as shown below.   

```{r}

t.test(mpg ~ am, data = mtcars)$p.value

```

To develop mathematical model between transition and **MPG** used linear regression.

## Modeling 

```{r}
model_1<- lm(mpg~factor(am), data = mtcars)
summary(model_1)
```
The manual transition care have 7.245 mpg than automatic car. But $R^2= 0.3598$ this mean only 0.3598% of mpg variance controlled by gear transmission types. Therefore need to add more variables related with ***MPG*** to increase predict confidence.  

```{r}
res <- cor(mtcars)
round(res, 2)
```
The correlation table show there are many variables strongly related to **MPG**.

Therefore must develop **MPG** mathematical model with many variables rather than one variable by using multiple linear regression. Because there are variable does not correlated with **MPG** therefore use **stepwise** function to determine best variable to develop **MPG** mathematical formula. 


```{r}
model_2<- step(lm(mpg ~ ., data = mtcars), trace=0)
summary(model_2)

```

## Conclusion

According to summary of multiple linear regression (with, qsec, am) beset variable to predict **MPG** with variance  0.8497 % based on p.value and $R^2$

* Increase care wight decrease **MPG** by $-3.9165*wt$ with probability $1- 2x6.95e^6$
* Increase care accerlation increase **MPG** by $1.2259*qsec$ with probability  $1-2x 0.000216$.
* Transition mode increase **MPG** by 2.9358 if manual or not effect if  automatic with probablity $1-2x0.046716$.

* the final formula is for **MPG**: $$mpg =9.6178 -3.9165wt + 1.2259qsec + 2.9358am + \epsilon$$

## Appendix

```{r}
boxplot(mpg ~ factor(mtcars$am,labels=c('Automatic','Manual')), 
        data=mtcars, 
        xlab="Transmission", 
        ylab="Miles per Gallon", 
        main="MPG vs. Transmission")
par(mfrow = c(2,2))
plot(model_2)

```